Supplementary material for `Kaggle-in-class Data Challenges can Boost Student Learning`

### 2018-04-10 paper-kaggle.Rmd
working through item analysis statistics

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(knitr)
library(bookdown)
library(knitcitations)
library(RefManageR)
library("tidyverse")
#library("ggpubr")
library("readxl")
library("gridExtra")

@@

scores_5242$`Exam Tot` <- apply(scores_5242[,4:27],1, sum, na.rm=T)
scores_2420$`Exam Tot` <- apply(scores_2420[,4:27],1, sum, na.rm=T)

scores_5242 <- scores_5242 %>% mutate(perf = `7b (8)`/`Exam Tot`)
scores_2420 <- scores_2420 %>% mutate(perf = `7b (8)`/`Exam Tot`)
scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
  filter(!is.na(perf))
scores_2420 <- scores_2420 %>% mutate(class="No") %>%
  filter(!is.na(perf))

@@

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(knitr)
library(bookdown)
library(knitcitations)
library(RefManageR)
library(tidyverse)
#library(ggpubr)
library(readxl)
library(gridExtra)

@@

scores_5242$`Exam Tot` <- apply(scores_5242[,4:27], 1, sum, na.rm=T)
scores_2420$`Exam Tot` <- apply(scores_2420[,4:27], 1, sum, na.rm=T)

scores_5242 <- scores_5242 %>% mutate(perf = ((`7b (8)`+ `7c (3)`)/11)/(`Exam Tot`/100))
scores_2420 <- scores_2420 %>% mutate(perf = ((`7b (8)`+ `7c (3)`)/11)/(`Exam Tot`/100))
scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
  filter(!is.na(perf))
scores_2420 <- scores_2420 %>% mutate(class="No") %>%
  filter(!is.na(perf))

@@

```{r eval=FALSE}
poss_marks <- c(4, 2, 2, 2, 3, 3, 9, 8, 5, 2, 2, 3, 3, 3, 2, 3, 3, 6, 10, 8, 3, 3, 3, 2, 4, 2)
scores_pct <- bind_rows(scores_2420, scores_5242)
scores_pct$group <- c(rep("2420", 145), rep("5242", 34))
scores_pct <- scores_pct %>% filter(!is.na(`9b (2)`))
for (i in 1:26)
  scores_pct[,i+1] <- scores_pct[,i+1]/poss_marks[i]

#div <- function(x) x/poss_marks
#scores_pct[,2:27] <- apply(scores_pct[,2:27], 1, div)
scores_pct_long <- scores_pct %>% gather(q, mark, -group, -id)
ggplot(scores_pct_long, aes(x=q, y=mark, colour=group)) + geom_boxplot()

# Difficulty
scores_pct_long %>% group_by(q) %>% 
  summarise(m=mean(mark)) %>% 
  arrange(m) %>% print(n=30)
# Discrimination
scores_pct_long %>% group_by(q) %>% 
  summarise(s=sd(mark)) %>% 
  arrange(desc(s)) %>% print(n=30)

scores_pct_m <- scores_pct %>% 
  group_by(group) %>% summarise_all(mean, na.rm=T) %>% select(-id)
scores_pct_s <- scores_pct %>% 
  group_by(group) %>% summarise_all(sd, na.rm=T) %>% select(-id)
scores_pct_s[1,-1] <- scores_pct_s[1,-1]/sqrt(140)*1.96
scores_pct_s[2,-1] <- scores_pct_s[2,-1]/sqrt(34)*1.96

ms <- bind_cols(gather(scores_pct_m, q, value, -group), 
                gather(scores_pct_s, q, value, -group)) %>%
  select(-group1, -q1) %>%
  rename(m=value, s=value1)
ggplot(ms, aes(x=q, y=m, colour=group)) + #geom_point(position="dodge") +
  geom_errorbar(aes(ymin=m-s, ymax=m+s), position="dodge")
```

```{r eval=FALSE}
scores_5242 <- scores_5242 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))
scores_2420 <- scores_2420 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))

scores_5242 <- scores_5242 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
scores_2420 <- scores_2420 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
  filter(!is.na(perf2))
scores_2420 <- scores_2420 %>% mutate(class="No") %>%
  filter(!is.na(perf2))
scores <- bind_rows(scores_5242, scores_2420)

ggplot(scores, aes(x=class, y=perf2)) + 
  geom_boxplot() + 
  xlab("Participated in competiton") +
  ylab("Standardized RE")
```

### 2018-04-10 supplementary.Rmd
working through item analysis statistics

```{r}
# read Unimelb data
# UniMelbData <- read_csv(file="data/UniMeldUnIndef.csv")
# UniMelbData <- UniMelbData %>% select(-LastName, -FirstName, -StudentID)
# write_csv(UniMelbData, path="data/deidentified_UMelb.csv")
UniMelbData <- read_csv(file="data/deidentified_UMelb.csv") #, header=TRUE, sep=",")
```

>>>>

```{r}
library(tidyverse)
library(gridExtra)
# read Unimelb data
# UniMelbData <- read_csv(file="data/UniMeldUnIndef.csv")
# UniMelbData <- UniMelbData %>% select(-LastName, -FirstName, -StudentID)
# write_csv(UniMelbData, path="data/deidentified_UMelb.csv")
UniMelbData <- read_csv(file="data/deidentified_UMelb.csv") #, header=TRUE, sep=",")
```
